---
title: "BMI Tool Introduction"
author: "Li Lv"
date: "Aug.18 2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- BMI Tool is one web based application developed by Shiny of RStudio. With this application, it is convenient to calculate the BMI (Body Mass Index) for any person, by providing weight and height. 
- This presentation is generated through R Presentation with output slidy_presentation to present a reproducible pitch information for the BMI Tool application.
- Both the BMI tool application and this presentation are created for Coursera course Developing Data Products week 4 assignment. 


## BMI Tool Design

- BMI (Body Mass Index) is a measure of body fat based on height and weight that applies to adult men and women.
- BMI is calculated by height and weight by function BMI=weight(Kg)/height(m)^2. See details in page BMI Calculation.
- As reference, the typical BMI categories list can be referred to check the corresponding body fat resutlt.
- The BMI categories list is described in page BMI Categories.


## BMI Tool with R Shiny

- The BMI Tool web based application is generated by Shiny in RStudio. Multiple Files(ui.R/server.R) is seleted.
- With designed BMI Tool, after entering your height and weight and clicking 'New BMI' button on left panel, the BMI result can be shown in right main panel.
- The typical BMI categories list is displayed on right main panel as well. That can help to check the body fat corresponding to the result BMI vlue.
- In ui.R, the input height and weight are created by sliderInput. The submitButton with name 'New BMI' is used to trigger recalculation by new input.
- In server.R, the BMI is calculated by input height and weight. The BMI categories table is defined and displayed.


## BMI Calculation

The two input variables are provided from UI, as Height in cm and Weight in Kg. The relevant BMI is resulted by Weight(Kg)/Height(m)^2.

The input variables are assumed as 165 cm and 50 Kg in below example.

```{r BMI Calculation, echo = TRUE}
    #input Height in cm, Weight in Kg
    Weight <- 50
    Height <- 165
    curBMI <- Weight / ((Height/100)^2)
    curBMI <- round(curBMI, 2)
    paste("Your BMI: ", curBMI, " kg/m^2")
```

## BMI Categories

The BMI Categories list is provided on UI as reference. That is helpful to understand the corresponding health status, as under weight, normal weight, over weight, or obesity.

```{r BMIList, echo=TRUE}
    BMICategories <- matrix(
      c("Under weight", "<=18.5",
        "Normal Weight", "18.5 ~ 24.9",
        "Over Weight", "25 ~ 29.9",
        "Obesity", ">=30"), 
      nrow=4, ncol=2, byrow=TRUE,
      dimnames=list(c("type1", "type2", "type3", "type4"), c("BMI Categories", "Range"))) 
    
    head(BMICategories, 4)
```

